\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/eval.tex
checkpointing at the beginning of 6.2

\subsection{Standard models}
\label{sec:shallow}
We consider three types of classifiers: linear, Na\"{i}ve Bayes, and decision trees. 
These classifiers are trained on the followinng data sets from the UCI  machine learning repository~\cite{uci}:
 the Wisconsin Breast Cancer data set, 
Credit Approval data set, Audiology (Standardized) data set, Nursery data set, and
ECG (electrocardiogram) classification data from~\cite{barni}.

The results for linear classification are in Table~\ref{tab:lc}. The input and model are both vectors of length $d$. The time in columns ``Prev. time'' and communication ``Prev.Comm'' is the time and total network communication reported in~\cite{shafindss}. They remark that these times are obtained by simulating a network with 40ms round trip time, which is the same as our WAN setting. The total execution time of \tool generated code in the LAN and the WAN setting is reported next followed by the total communication.
We observe that \tool generated code has performance competitive to~\cite{shafindss}.
The execution time is dominated by multiplications and boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the benchmarks as they reflect the number of and gates required for a single 32-bit integer comparison with zero. The number of multiplication gates (\#Mul) is the same as the model size $d$. The last column shows the lines of code of \tool program, which is also independent of the model size.

@@

\begin{table*}
\begin{tabular}{c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$  & Prev. time (s) & Prev. Comm (kb) & LAN time (s) & WAN time (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25 & 95 & 30 & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36 & 95 & 47 & 795 & 20\\
\hline
\end{tabular}

>>>>

\subsection{Standard classifiers}
\label{sec:shallow}
We train the three standard classifiers, linear, Na\"{i}ve Bayes, and
decision trees, on the following data sets from the UCI
machine learning repository~\cite{uci}:
 the Wisconsin Breast Cancer data set, 
Credit Approval data set, Audiology (Standardized) data set, Nursery
data set, and ECG (electrocardiogram) classification data
from~\cite{barni}.

The results for linear classification are in Table~\ref{tab:lc}. The
input and model are both vectors of length $d$. The time in columns
``Prev. time'' and communication ``Prev. comm'' is the time and total
network communication reported by Bost et al.~\cite{shafindss}. They
report these numbers over a simulated network with 40ms
round trip
time, which is same as our WAN setting. The total execution time
of \tool generated code in the LAN and the WAN setting is reported
next, followed by the total communication.
We observe that \tool generated code has performance competitive
to~\cite{shafindss}.
The execution time is dominated by multiplications and boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the
benchmarks as they reflect the number of and gates required for a
single 32-bit integer comparison with zero. The number of
multiplication gates (\#Mul) is the same as the model size $d$. The
last column shows the lines of code of \tool program, which is also
independent of the model size.

@@

\begin{table*}
\begin{tabular}{c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$  & Prev. time (s) & Prev. comm (kb) & LAN time (s) & WAN time (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25 & 95 & 30 & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36 & 95 & 47 & 795 & 20\\
\hline
\end{tabular}
